Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-25 paper/paper.qmd
final paper updates

portrait_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Frequency", y = "Word")

dalloway_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Frequency", y = "Word")

swann_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Frequency", y = "Word")

prufrock_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Frequency", y = "Word")

bliss_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Frequency", y = "Word")

>>>>

portrait_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Count", y = "Word")

dalloway_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Count", y = "Word")

swann_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Count", y = "Word")

prufrock_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Count", y = "Word")

bliss_words |> head(20) |>
ggplot(aes(x = n, y = reorder(word, n))) +
  geom_bar(stat = "identity", fill = "steelblue4") +
  geom_text(aes(label = n), hjust = -0.3, vjust = 0.5, color = "grey40", size = 3) +
  labs(x = "Count", y = "Word")
